---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
p {
  font-size: 15px; 
  font-family: Georgia, serif;
}
body {
  background-color: #fae2c0;
  max-width: 900px;
  margin: 0 auto;
  text-align: center;
  font-family: 'Helvetica', sans-serif;
}
h2 {
  color: #2d2390;
  font-family: Georgia, serif;
}
h3 {
  color: #cc3366;
  font-family: Georgia, serif;
}
```

## This report explores the music listening habits of students, based on survey responses.



```{r}

library(tidyverse)


logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQausqscgIzW3jvmcQm2cMwiJUbUAwoS_H7Oye6rqbLfD2wadupUR6j6xgw2aLCKW4HgBg0pU8xx3ha/pub?gid=1942138870&single=true&output=csv")

latest_data <- logged_data %>%
  rename(
    timestamp = `Timestamp`,
    hours_per_week = `Approximately, how many hours a week do you listen to music?`,
    genre = `What genre of music do you frequently listen to?`,
    device = `What do you use when listening to music?`,
    place = `Where do you most often listen to music?`
  )


most_popular_genre <- names(sort(table(latest_data$genre), decreasing = TRUE))[1]
most_popular_device <- names(sort(table(latest_data$device), decreasing = TRUE))[1]

```

###  Summary of the Student Music Survey

The most popular genre is **`r names(sort(table(latest_data$genre), decreasing = TRUE))[1]`**.

On average, students listen to music for **`r round(mean(latest_data$hours_per_week), 1)`** hours per week.

The maximum listening time is **`r max(latest_data$hours_per_week)`** hours per week/

# Bar Charts

```{r genre-plot, echo=FALSE, fig.width=11, fig.height=5}
# genre plot
genre_plot <- ggplot(data = latest_data) +
  geom_bar(aes(x = genre, fill = genre)) +
  labs(title = "Most Frequently Listened Music Genres",
       caption = "Student Music Survey",
       x = "Genre",
       y = "Number of Students") +
  scale_fill_discrete(guide = FALSE)
paste("Shows genre listened to by students")
genre_plot
```


```{r device_plot, echo=FALSE, fig.width=11, fig.height=5}
# device plot
device_plot <- ggplot(data = latest_data) +
  geom_bar(aes(x = device, fill = device)) +
  labs(title = "Devices Used When Listening to Music",
       caption = "Student Music Survey",
       x = "Device",
       y = "Number of Students") +
  scale_fill_discrete(guide = FALSE)
paste("Shows listening devices used to by students")
device_plot
```


```{r place_plot, echo=FALSE, fig.width=11, fig.height=5}
# place plot
place_plot <- ggplot(data = latest_data) +
  geom_bar(aes(x = place, fill = place)) +
  labs(title = "Where Students Most Often Listen to Music",
       caption = "Student Music Survey",
       x = "Place",
       y = "Number of Students") +
    scale_fill_discrete(guide = FALSE)

paste("Shows where students are likely to listen to music from")
place_plot
```


